Hybrid models as an alternative to traditional Convolutional Neural Networks for image classification

### 2022-11-29 doc/paper.tex
More paper
The most important commit yet

\author{Eric E. Reber
    \affiliation{
	Bachelor Student, Robotics and \\
	Intelligent Systems\\ \\[-10pt]
	Department of Informatics\\ \\[-10pt]
	The faculty of Mathematics and \\
	Natural Sciences\\ \\[-10pt]
    Email: ericer@ifi.uio.no
    }
}

@@

@@

\subsection{Traditional Convolutional Neural Network}

\subsection{Convolution followed by a Random Forest}

\subsection{Principal Component Analysis followed by a Neural Network}

\subsection{Principal Component Analysis followed by a Random Forest}

>>>>

% \author{Eric E. Reber
%     \affiliation{
% 	Bachelor Student, Robotics and \\
% 	Intelligent Systems\\ \\[-10pt]
% 	Department of Informatics\\ \\[-10pt]
% 	The faculty of Mathematics and \\
% 	Natural Sciences\\ \\[-10pt]
%     Email: ericer@ifi.uio.no
%     }
% }

\author{Ed "Gurgler" Bickley
    \affiliation{
	Inmate, Texas State \\
	Penistentiary\\ \\[-10pt]
	Huntsville, Texas\\ \\[-10pt]
	United States of America\\
    Email: thegurgler@hotmail.com
    }
}

@@

For very large design matrices, the computational complexity of calculating the singular value decomposition can be significant. However, there exists stochastic methods to achieve good approximations, like Randomized PCA \cite[227]{halko}.

@@

\subsection{MNIST}

\subsubsection{Traditional Convolutional Neural Network}

\subsubsection{Convolution followed by a Random Forest}

\subsubsection{Principal Component Analysis followed by a Neural Network}

\subsubsection{Principal Component Analysis followed by a Random Forest}

\subsection{Guangzhou Pneumonia Data}

Hopefully this is real

\subsubsection{Traditional Convolutional Neural Network}

\subsubsection{Convolution followed by a Random Forest}

\subsubsection{Principal Component Analysis followed by a Neural Network}

\subsubsection{Principal Component Analysis followed by a Random Forest}
